Development Of Parallel Matrix Operations

### 2011-02-15 paper/paper.tex
Merge

@@

\section{Results}
\subsection{Matrix-Vector Multiplication}

@@

@@

@@

@@

>>>>

\begin{verbatim}
MatrixInt A = ...
VectorInt B = ...
Matrix C = MatrixOp.mult(A,B)
Matrix C = MatrixParallelOp.mult(A,B)

\end{verbatim}

@@

\section{Results}

@@

\begin{center}
\includegraphics[scale=0.5]{images/matrix-vector/running-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/matrix-vector/speedup-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/matrix-vector/esdf-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/matrix-vector/eff-vs-proc.png}
\end{center}

@@

\begin{center}
\includegraphics[scale=0.5]{images/parallel/run-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/parallel/speedup-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/parallel/edsf-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/parallel/eff-vs-proc.png}
\end{center}

@@

\begin{center}
\includegraphics[scale=0.5]{images/parallel-stras/running-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/parallel-stras/speedup-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/parallel-stras/edsf-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/parallel-stras/eff-vs-proc.png}
\end{center}

@@

\begin{center}
\includegraphics[scale=0.5]{images/matrix-inversion/running-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/matrix-inversion/speedup-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/matrix-inversion/edsf-vs-proc.png}
\end{center}
\begin{center}
\includegraphics[scale=0.5]{images/matrix-inversion/eff-vs-proc.png}
\end{center}
